GBM Recurrence - Mine Single Cell data

### 2023-08-26 reports/gbm_recurrence_mine_single_cell_data_visualization.qmd
single_cell_asah1_expression_v2
sc_asah1_expression_violin

```{r}
View(annotated_with_asah1)
```

@@

```{r}
cell_type_centroid <- annotated_with_asah1 %>%
  group_by(cluster) %>%
  summarise(x = mean(x), 
            y = mean(y)) %>%
  ungroup()

  cell_type_centroid
```

@@

```{r}
umap_cell_type
```

@@

>>>>

@@

```{r}
cell_type_centroid <- annotated_with_asah1 %>%
  group_by(cluster) %>%
  summarise(x = mean(x), 
            y = mean(y)) %>%
  ungroup()
```

@@

@@

# Violin plot

```{r}
annotated_with_asah14violin <- annotated_with_asah1 %>%
  filter(asah1_expression > 2.5) 
```

```{r}
violin_asahl_expr_celltype <- ggplot(annotated_with_asah14violin, 
       aes(x = cluster, 
           y = asah1_expression,
           fill = cluster)) +
  geom_violin() +
  #scale_color_gradient(low = "yellow", high = "red") +
  labs(x = "Cell type", 
       y = "ASAH1 expression [log2(CPM)]") +
  theme(legend.position = "none",
        # tilt the x-axis labels 45 degrees
        axis.text.x = element_text(angle = -45, 
                                   hjust = 0,
                                   vjust = 1.6)
        ) 
```

```{r}
violin_asahl_expr_celltype
```

```{r}
umap_grid_w_violin <- plot_grid(umap_cell_type, 
                                umap_asah1_expr, 
                                violin_asahl_expr_celltype,
                                ncol = 2)
```

```{r fig.width=20, fig.height=10}
umap_grid_w_violin
```

```{r}
ggsave(here::here("figures/umap_grid_asah1_expression_violin_scRNAseq.pdf"), 
       umap_grid_w_violin, 
       width = 34, 
       height = 34,
       units = "cm")
```

```{r}
ggsave(here::here("figures/umap_grid_asah1_expression_violin_scRNAseq.png"), 
       umap_grid_w_violin, 
       width = 34, 
       height = 34,
       units = "cm")
```
